\documentclass[font = 23,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\name{Tyler} {Lukasiewicz}
\phone[mobile]{(561)~512~0837}
\email{tlukasiewicz@knights.ucf.edu}
\email{tlukasiewicz@hackucf.org}
\homepage{www.kabla.me/blog}
\extrainfo{https://www.github.com/kablaa}
\date{}
\setlength{\textheight}{8.5in}
\setlength{\topmargin}{0.5in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\textwidth}{6.5in}
\linespread{1.5}

\begin{document}
\maketitle

\section{Languages}
C/C++, Python, Assembly (x86, x64, and ARM), Java
        
\section{Internships}
\label{sec:Internships}
\begin{itemize}
    \item Summer 2016: Raytheon SI Government Solutions
        \begin{itemize}
            \item Did vulnerability Research on Qualcomm's TrustZone for Android 
                \begin{itemize}
                        \item Worked on Reverse Engineering the TrustZone kernel on the Nexus 5 and Nexus 6 

                        \item Developed a Fuzzer in python that will send commands to TrustZone and record responses from kernel functions 
                \end{itemize}
            \item  Day to day activities involved: 
            \begin{itemize} 
                \item Extensive Reverse Engineering in IDA 
                \item Writing Idapython scripts to expedite research 
                \item Research on previously released TrustZone exploits 
                \item Documentation of progress 
                \item Fuzzer development. 
            \end{itemize}
        \end{itemize}
\end{itemize}

\section{Hacking As A (Legal) Hobby} 
    \begin{itemize}

        \item Elected Vice President of HackUCF \url{https://www.hackucf.org} (2016-2017), a nationally recognized cyber security club. 

        \item Captain of UCF's offensive security team, Knightsec
        
        \item Lead Capture the Flag (CTF) workshops, in which 50-60 students learned the essentials of binary exploitation and reverse engineering. 
            Topics include working in the Linux environment, x86 assembly, debugging with GDB and IDA, buffer overflows, Return Oriented Programming, writing shellcode, shellcode injection, heap exploitation, socket programming, and python scripting. 
        
        \item Wrote 10 binary exploitation challenges for school-wide CTF \url{https://ctf.hackucf.org}. Challenges cover Reverse Engineering, Buffer-Overflow, shellcode, and ROP.

        \item Wrote, recorded, and edited x86 Assembly Instructional video for HackUCF. 
        \begin{itemize}
            \item \url{httpss://youtu.be/75gBFiFtAb8} 
        \end{itemize}

        \item  Participated in several Capture the Flag competitions
        \begin{itemize}
            \item writeups available at \url{https://kabla.me/blog/writeups} 

        \end{itemize}
        
    \item Experience managing https server for personal website and school-wide CTF. 
        \begin{itemize}
            \item LAMP
            \item IpTables
            \item Docker
        \end{itemize}
    
    \end{itemize}

\section {Research} 
        Collaborating with a multi disciplined Big Data analysis team from The University of Central Florida (under the direction of Dr. Jun Wang) to produce 
            numerous technical publication and grant applications. Served as a paid technical writer/editor on the team. Publications available on personal website.
            \begin{itemize}
                \item Sebo: Selective Bulk Analysis Optimization in Big Data Processing. 
                    \begin{itemize}
                        \item NMC PRObE 
                    \end{itemize}
                \item OPAS:Analysis and Optimization of Parallel Data Access on Distributed File Systems
                    \begin{itemize}
                        \item IEEE
                    \end{itemize}
                \item SLAM: Scalable Locality-Aware Middleware for I/O in Scientic Analysis and Visualization
                    \begin{itemize}
                        \item NMC PRObE 
                    \end{itemize}
            \end{itemize}

\section{Education}
    BS in Mathematics from The University of Central Florida, 3.2 GPA (references available upon request) 
\end{document}

